---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# ffmpegR

[![license](https://img.shields.io/badge/license-GPL--3-blue.svg)](https://www.gnu.org/licenses/gpl-3.0.en.html)

These are functions to do common video editing operations in [ffmpeg](ffmpeg.org) through R. 

Works on macOS only for now. Windows support wouldn't be difficult to add, and 
I'll consider it if anyone shows some interest. 

### Installation

```{r eval = F}
devtools::install_github("nicholascarey/ffmpegR")
```

### Functions

Currently there are three functions:

#### `trim_vid`

Simply trims a video between two timepoints. 

```{r eval = F}
 trim_vid(dir = "path/to/directory", # location, if not in current working directory
          file = "input_file.mp4", # name of file including extension
          output = "output", # name of output file
          from = "00:02:45", # trim from here...
          to = "00:09:15") # ...to here
```

#### `join_vid`

Joins two videos together into one file. 

```{r eval = F}
join_vid(dir = "path/to/directory", # working directory
         file1 = "input_file_1.mp4", # file 1
         file2 = "input_file_2.mp4", # file 2 
         output = "output") # name of output file
```

#### `remove_fisheye`

Removes the 'fisheye' effect from GoPro Hero 5 Black videos (other models to follow....)

```{r eval = F}
 remove_fisheye(file = "path/to/file", # input
                dir = "path/to/dir", # directory
                output = "output", # output
                remove_audio = FALSE) # remove the audio?
```




